An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-18 jmiv.tex
Notation adjusts

In other words, each flow iteration decides which pixels in the inner boundary are to be removed from \revision{$S^{(i)}$} and which are to be kept in \revision{$S^{(i)}$}. We recall the definition of our digital curvature estimator:
\begin{align}
	\hat{\kappa}^2(p) &= c_1\Big( c_2 - | B_r(p) \cap S^{\revision{(i)}} | \Big)^2, 
	\label{eq:curvature-estimator-pixels}
\end{align}
where $c_1=3/r^6$ and $c_2=\pi r^2/2$.

@@

\revision{
\begin{align*}
	F_r^{(i)}(p) &:= \big( S^{(i)} \setminus I^{(i)} \big) \cap B_r(p)\\
	I_r^{(i)}(p) &:= I^{(i)} \cap B_r(p) \\
	X_r^{(i)}(p) &:= X\big( I_r^{(i)}(p) \big).
\end{align*}
}

@@

Length and \revision{data} terms should be properly defined in order to comply with the complement step of the DCE
algorithm. The length penalization is defined as
\begin{align}
  s(x)=\sum_{x_j \in \mathcal{N}_4(x)}{ t(x_j) }, \quad \text{where } t(x_j) = \left\{\begin{array}{ll}
  (x-x_j)^2, & \text{if } x_j \in X_{r}^{(i)}\\
  (x-0), & \text{if } x_j \in F_{r}^{(i)}\\
  (x-1), & \text{otherwise }
  \end{array}\right.
  \label{eq:length-penalization}
\end{align}

@@

\begin{align}
  g(y) = -(1-y)\log{G_f(I(y))} - y\log{G_b(I(y))}.
  \label{eq:data-fidelity}
\end{align}

>>>>

In other words, each flow iteration decides which pixels in the inner boundary are to be removed from \revision{$S^{(i)}$} and which are to be kept in \revision{$S^{(i)}$}. We recall the definition of the II digital curvature estimator:
\begin{align}
	\hat{\kappa}^2(p) &= c_1\Big( c_2 - | B_r(p) \cap S^{\revision{(i)}} | \Big)^2, 
	\label{eq:curvature-estimator-pixels}
\end{align}
where $c_1=3/r^6$ and $c_2=\pi r^2/2$.

@@

\revision{
\begin{align*}
	F^{(i)} &:= S^{(i)} \setminus I^{(i)} \\
	F_r^{(i)}(p) &:= F^{(i)} \cap B_r(p)\\
	I_r^{(i)}(p) &:= I^{(i)} \cap B_r(p) \\
	X_r^{(i)}(p) &:= X\big( I_r^{(i)}(p) \big).
\end{align*}
}

@@

Length and \revision{data} terms should be properly defined in order to comply with the complement step of the DCE
algorithm. The length penalization is defined as
\revision{
\begin{align}
  s(x_{w(p)})=\sum_{q \in \mathcal{N}_4(p)}{ t(q) }, \quad \text{where } t(q) = \left\{\begin{array}{ll}
  (x_{w(p)}-x_{w(q)})^2, & \text{if } q \in I^{(i)}\\
  (x_{w(p)}-0), & \text{if } q \in F^{(i)}\\
  (x_{w(p)}-1), & \text{otherwise }
  \end{array}\right.
  \label{eq:length-penalization}
\end{align}}

@@

\begin{align}
  g(\revision{x_{w(p)}}) = -(1-\revision{x_{w(p)}})\log{G_f(p)} - \revision{x_{w(p)}}\log{G_b(p)}.
  \label{eq:data-fidelity}
\end{align}
